---
title: "Simulation 1: Woman without FP"
author: "JBF"
date: "11/1/2016"
output: html_document
---

* Nsim = `r Nsim` of simulation runs
* N = `r N` of women in each study

Hypothesis:

* Time up to pre-clinical Weibull
* Sojourn time is an exponencial (0.25)
* Time to enter is an Uniform(0, 15)
* Time scale: years-50

```{r, echo = F}
options(width = 250)
library(msm)
library(dplyr)
library(DT)
library(ggplot2)
source("~/PhD/aux_fun.R")
aux_scale <- (1/scale_param)^shape_param
exp_param <- 0.25
msm_50_al <- lapply(msm_50, function(.mod) .mod$mod_al)
msm_50_ob <- lapply(msm_50, function(.mod) .mod$mod_ob)
msm_50_no <- lapply(msm_50, function(.mod) .mod$mod_no)
msm_50_si <- lapply(msm_50, function(.mod) .mod$mod_si)
msm_50_4_al <- lapply(msm_50_4, function(.mod) .mod$mod_al)
msm_50_4_ob <- lapply(msm_50_4, function(.mod) .mod$mod_ob)
msm_50_4_no <- lapply(msm_50_4, function(.mod) .mod$mod_no)
msm_50_4_si <- lapply(msm_50_4, function(.mod) .mod$mod_si)
msm_left_al <- lapply(msm_left, function(.mod) .mod$mod_al)
msm_left_ob <- lapply(msm_left, function(.mod) .mod$mod_ob)
msm_left_no <- lapply(msm_left, function(.mod) .mod$mod_no)
msm_left_si <- lapply(msm_left, function(.mod) .mod$mod_si)
msm_left_4_al <- lapply(msm_left_4, function(.mod) .mod$mod_al)
msm_left_4_ob <- lapply(msm_left_4, function(.mod) .mod$mod_ob)
msm_left_4_no <- lapply(msm_left_4, function(.mod) .mod$mod_no)
msm_left_4_si <- lapply(msm_left_4, function(.mod) .mod$mod_si)
```

Parameters:

* Shape parameter = `r shape_param`
* Scale parameter = `r round(aux_scale, 6)`
* Exponential parameter = `r exp_param`

# Outputs
## 3-state model
### Complet
```{r, echo = F}
t.com <- data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                    print_qtrans(msm_50_al, 't1', 1, 2, aux_scale)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                    print_qtrans(msm_50_al, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                    print_qtrans(msm_50_al, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                    print_qtrans(msm_50_al, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_50_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_50_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_50_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_al, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_left_al, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_left_al, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_left_al, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_left_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_left_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_left_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_al, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_50_4_al, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_50_4_al, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_al, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_50_4_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_50_4_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_al, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                      print_qtrans(msm_left_4_al, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                      print_qtrans(msm_left_4_al, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_al, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[05, 10)',
                      print_qtrans(msm_left_4_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[10, 15)',
                      print_qtrans(msm_left_4_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_al, 't4', 2, 3, exp_param)))

t.com %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, pci, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

dgraf <- data.frame(times = 1:20, 
                    ncrib = rep(c(rep('theoric', 20), rep(10, 2*20), rep(4, 2*20)), 2),
                    left = rep(c(rep('theoric', 20), rep(rep(c(F, T), each = 20), 2)), 2),
                    trans = rep(c('1 -> 2', '2 -> 3'), each = 100),
                    hazard = c((shape_param/scale_param)*(1:20/scale_param)^(shape_param - 1),
                               rep(t.com$median[1:4], each = 5),
                               rep(t.com$median[9:12], each = 5),
                               rep(t.com$median[17:20], each = 5),
                               rep(t.com$median[25:28], each = 5),
                               rep(exp_param, 20),
                               c(rep(t.com$median[5:8], each = 5)),
                               c(rep(t.com$median[13:16], each = 5)),
                               c(rep(t.com$median[21:24], each = 5)),
                               c(rep(t.com$median[29:32], each = 5))))
dgraf$ncrib <- relevel(dgraf$ncrib, ref = 'theoric')
dgraf$left <- relevel(dgraf$left, ref = 'theoric')
ggplot(dgraf, aes(x = times, y = hazard, col = ncrib, lty = left)) + geom_line() + 
  facet_grid(trans ~ ., scales = "free")
```

### Observat
```{r,echo=F}
t.obs <- data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                    print_qtrans(msm_50_ob, 't1', 1, 2, aux_scale)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                    print_qtrans(msm_50_ob, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                    print_qtrans(msm_50_ob, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                    print_qtrans(msm_50_ob, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_50_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_50_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_50_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_ob, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_left_ob, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_left_ob, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_left_ob, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_left_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_left_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_left_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_ob, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_50_4_ob, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_50_4_ob, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_ob, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[05, 10)',
                       print_qtrans(msm_50_4_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[10, 15)',
                       print_qtrans(msm_50_4_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '2 -> 3', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_ob, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                      print_qtrans(msm_left_4_ob, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                      print_qtrans(msm_left_4_ob, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_ob, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[05, 10)',
                      print_qtrans(msm_left_4_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[10, 15)',
                      print_qtrans(msm_left_4_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '2 -> 3', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_ob, 't4', 2, 3, exp_param)))

t.obs %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

dgraf <- data.frame(times = 1:20, 
                    ncrib = rep(c(rep('theoric', 20), rep(10, 2*20), rep(4, 2*20)), 2),
                    left = rep(c(rep('theoric', 20), rep(rep(c(F, T), each = 20), 2)), 2),
                    trans = rep(c('1 -> 2', '2 -> 3'), each = 100),
                    hazard = c((shape_param/scale_param)*(1:20/scale_param)^(shape_param - 1),
                               rep(t.obs$median[1:4], each = 5),
                               rep(t.obs$median[9:12], each = 5),
                               rep(t.obs$median[17:20], each = 5),
                               rep(t.obs$median[25:28], each = 5),
                               rep(exp_param, 20),
                               c(rep(t.obs$median[5:8], each = 5)),
                               c(rep(t.obs$median[13:16], each = 5)),
                               c(rep(t.obs$median[21:24], each = 5)),
                               c(rep(t.obs$median[29:32], each = 5))))
dgraf$ncrib <- relevel(dgraf$ncrib, ref = 'theoric')
dgraf$left <- relevel(dgraf$left, ref = 'theoric')
ggplot(dgraf, aes(x = times, y = hazard, col = ncrib, lty = left)) + geom_line() + 
  facet_grid(trans ~ ., scales = "free")
```

## 2-state model
### Model with event as SCD or IC. Time up to IC.
```{r,echo=F}
t.no <- data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                   print_qtrans(msm_50_no, 't1', 1, 2, aux_scale)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                   print_qtrans(msm_50_no, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                   print_qtrans(msm_50_no, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                   print_qtrans(msm_50_no, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_no, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_left_no, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_left_no, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_left_no, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_no, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_50_4_no, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_50_4_no, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_no, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_no, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                      print_qtrans(msm_left_4_no, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                      print_qtrans(msm_left_4_no, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_no, 't4', 1, 2, aux_scale)))

t.no %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

### Model with event as SCD or IC. Time up to next mamography.
```{r,echo = F}
t.si <- data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                   print_qtrans(msm_50_si, 't1', 1, 2, aux_scale)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                   print_qtrans(msm_50_si, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                   print_qtrans(msm_50_si, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                   print_qtrans(msm_50_si, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_left_si, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_left_si, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_left_si, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_left_si, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[-Inf, 5)',
                       print_qtrans(msm_50_4_si, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[05, 10)',
                       print_qtrans(msm_50_4_si, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[10, 15)',
                       print_qtrans(msm_50_4_si, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = '1 -> 2', pci = '[15, Inf)',
                       print_qtrans(msm_50_4_si, 't4', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[-Inf, 5)',
                      print_qtrans(msm_left_4_si, 't1', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[05, 10)',
                      print_qtrans(msm_left_4_si, 't2', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[10, 15)',
                      print_qtrans(msm_left_4_si, 't3', 1, 2, aux_scale))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = '1 -> 2', pci = '[15, Inf)',
                      print_qtrans(msm_left_4_si, 't4', 1, 2, aux_scale)))

t.si %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```