---
title: "Simulation 3: FP as step function"
author: "JBF"
date: "11/1/2016"
output: html_document
---

```{r, echo = F}
options(width = 250)
library(gridExtra)
library(msm)
library(dplyr)
library(DT)
library(ggplot2)
source("~/PhD/aux_fun.R")
aux_scale <- (1/scale_param)^shape_param
exp_param <- 0.25
msm_50_al <- lapply(msm_50, function(.mod) .mod$mod_al)
msm_50_ob <- lapply(msm_50, function(.mod) .mod$mod_ob)
msm_50_no <- lapply(msm_50, function(.mod) .mod$mod_no)
msm_50_si <- lapply(msm_50, function(.mod) .mod$mod_si)
msm_50_4_al <- lapply(msm_50_4, function(.mod) .mod$mod_al)
msm_50_4_ob <- lapply(msm_50_4, function(.mod) .mod$mod_ob)
msm_50_4_no <- lapply(msm_50_4, function(.mod) .mod$mod_no)
msm_50_4_si <- lapply(msm_50_4, function(.mod) .mod$mod_si)
msm_left_al <- lapply(msm_left, function(.mod) .mod$mod_al)
msm_left_ob <- lapply(msm_left, function(.mod) .mod$mod_ob)
msm_left_no <- lapply(msm_left, function(.mod) .mod$mod_no)
msm_left_si <- lapply(msm_left, function(.mod) .mod$mod_si)
msm_left_4_al <- lapply(msm_left_4, function(.mod) .mod$mod_al)
msm_left_4_ob <- lapply(msm_left_4, function(.mod) .mod$mod_ob)
msm_left_4_no <- lapply(msm_left_4, function(.mod) .mod$mod_no)
msm_left_4_si <- lapply(msm_left_4, function(.mod) .mod$mod_si)
cox_50_al <- lapply(cox_50, function(.mod) .mod$mod_al)
cox_50_ob <- lapply(cox_50, function(.mod) .mod$mod_ob)
cox_50_no <- lapply(cox_50, function(.mod) .mod$mod_no)
cox_50_si <- lapply(cox_50, function(.mod) .mod$mod_si)
cox_50_4_al <- lapply(cox_50_4, function(.mod) .mod$mod_al)
cox_50_4_ob <- lapply(cox_50_4, function(.mod) .mod$mod_ob)
cox_50_4_no <- lapply(cox_50_4, function(.mod) .mod$mod_no)
cox_50_4_si <- lapply(cox_50_4, function(.mod) .mod$mod_si)
cox_left_al <- lapply(cox_left, function(.mod) .mod$mod_al)
cox_left_ob <- lapply(cox_left, function(.mod) .mod$mod_ob)
cox_left_no <- lapply(cox_left, function(.mod) .mod$mod_no)
cox_left_si <- lapply(cox_left, function(.mod) .mod$mod_si)
cox_left_4_al <- lapply(cox_left_4, function(.mod) .mod$mod_al)
cox_left_4_ob <- lapply(cox_left_4, function(.mod) .mod$mod_ob)
cox_left_4_no <- lapply(cox_left_4, function(.mod) .mod$mod_no)
cox_left_4_si <- lapply(cox_left_4, function(.mod) .mod$mod_si)
disc_50_al <- lapply(disc_50, function(.mod) .mod$mod_al)
disc_50_ob <- lapply(disc_50, function(.mod) .mod$mod_ob)
disc_50_no <- lapply(disc_50, function(.mod) .mod$mod_no)
disc_50_si <- lapply(disc_50, function(.mod) .mod$mod_si)
disc_50_4_al <- lapply(disc_50_4, function(.mod) .mod$mod_al)
disc_50_4_ob <- lapply(disc_50_4, function(.mod) .mod$mod_ob)
disc_50_4_no <- lapply(disc_50_4, function(.mod) .mod$mod_no)
disc_50_4_si <- lapply(disc_50_4, function(.mod) .mod$mod_si)
disc_left_al <- lapply(disc_left, function(.mod) .mod$mod_al)
disc_left_ob <- lapply(disc_left, function(.mod) .mod$mod_ob)
disc_left_no <- lapply(disc_left, function(.mod) .mod$mod_no)
disc_left_si <- lapply(disc_left, function(.mod) .mod$mod_si)
disc_left_4_al <- lapply(disc_left_4, function(.mod) .mod$mod_al)
disc_left_4_ob <- lapply(disc_left_4, function(.mod) .mod$mod_ob)
disc_left_4_no <- lapply(disc_left_4, function(.mod) .mod$mod_no)
disc_left_4_si <- lapply(disc_left_4, function(.mod) .mod$mod_si)
```

* Nsim = `r length(msm_50_al)` of simulation runs
* N = `r N` of women in each study

Hypothesis:

* Time up to pre-clinical Weibull
* Sojourn time is an exponencial (0.25)
* Time to enter is an Uniform(0, 15)
* Time scale: years-50

Parameters:

* Shape parameter = `r shape_param`
* Scale parameter = `r round(aux_scale, 6)`
* HR(FP) = `r HR_FP`
* Exponential = `r exp_param`

## Outputs
## Model 3 estats
### Complet
```{r, echo = F}
pt_tall <- c(2, 6, 10, 14, 18)
trans12 <- (shape_param/scale_param)*(pt_tall/scale_param)^(shape_param - 1)
t.com <- data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                    print_qtrans(msm_50_al, 't1', 1, 2, trans12[1])) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                    print_qtrans(msm_50_al, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                    print_qtrans(msm_50_al, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                    print_qtrans(msm_50_al, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                    print_qtrans(msm_50_al, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_al, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_50_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_50_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_50_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_50_al, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_50_al, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_al, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_left_al, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_left_al, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_left_al, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_left_al, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_al, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_left_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_left_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_left_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_left_al, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_left_al, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_al, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_50_4_al, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_50_4_al, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_50_4_al, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_al, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_50_4_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_50_4_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_50_4_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_al, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_50_4_al, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_al, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                      print_qtrans(msm_left_4_al, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                      print_qtrans(msm_left_4_al, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                      print_qtrans(msm_left_4_al, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_al, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_al, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[04, 08)',
                      print_qtrans(msm_left_4_al, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[08, 12)',
                      print_qtrans(msm_left_4_al, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[12, 16)',
                      print_qtrans(msm_left_4_al, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_al, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_left_4_al, 2, 1)))

t.com %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

t.com %>% filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

dgraf <- data.frame(Age = c(seq(51, 70, 0.1), rep(51:70, 9)), 
                    Transition = c(rep('Theoretical', 191), rep(10, 2*20), rep(4, 2*20),
                                   rep('Theoretical', 20), rep(10, 2*20), rep(4, 2*20)),
                    Left = c(rep('Theoretical', 191), rep(rep(c('No', 'Yes'), each = 20), 2),
                             rep('Theoretical', 20), rep(rep(c('No', 'Yes'), each = 20), 2)),
                    trans = rep(c('S0 -> Sp', 'Sp -> Sc'), c(271, 100)),
                    hazard = c((shape_param/scale_param)*(seq(1, 20, 0.1)/
                                                            scale_param)^(shape_param - 1),
                               rep(t.com$median[1:5], c(3:4, 4, 4:5)),
                               rep(t.com$median[13:17], c(3:4, 4, 4:5)),
                               rep(t.com$median[25:29], c(3:4, 4, 4:5)),
                               rep(t.com$median[37:41], c(3:4, 4, 4:5)),
                               rep(exp_param, 20),
                               rep(t.com$median[7:11], c(3:4, 4, 4:5)),
                               rep(t.com$median[19:23], c(3:4, 4, 4:5)),
                               rep(t.com$median[31:35], c(3:4, 4, 4:5)),
                               rep(t.com$median[43:47], c(3:4, 4, 4:5))))
dgraf$Transition <- relevel(dgraf$Transition, ref = 'Theoretical')
dgraf$Left <- relevel(dgraf$Left, ref = 'Theoretical')
# ggplot(dgraf, aes(x = Age, y = hazard, col = Transition, lty = Left)) + geom_step() + 
#   facet_grid(trans ~ ., scales = "free")
grid.arrange(ggplot(dgraf %>% filter(trans == 'S0 -> Sp'),
                    aes(x = Age, y = hazard, lty = Left, color = Transition)) + geom_step() +
               ylim(0, 0.0021) + labs(y = 'Transition rate S0 -> Sp') +
               theme(legend.position = "none"),
             ggplot(dgraf %>% filter(trans == 'Sp -> Sc'),
                    aes(x = Age, y = hazard, lty = Left, color = Transition)) + geom_step() +
               ylim(0, 0.3) + labs(lty = 'Truncation', y = 'Transition rate Sp -> Sc'),
             nrow = 1)
tiff(filename = "fig_1.tiff", width = 20, height = 15, units = 'cm', res = 300)
grid.arrange(ggplot(dgraf %>% filter(trans == 'S0 -> Sp', Transition != 4),
                    aes(x = Age, y = hazard, lty = Left)) + geom_step() + ylim(0, 0.0021) +
               labs(y = 'Transition rate S0 -> Sp') + theme(legend.position = "none"),
             ggplot(dgraf %>% filter(trans == 'Sp -> Sc', Transition != 4),
                    aes(x = Age, y = hazard, lty = Left)) + geom_step() + ylim(0, 0.3) +
               labs(lty = 'Late Entry', y = 'Transition rate Sp -> Sc'),
             nrow = 1)
dev.off()
```

### Observat
```{r, echo = F}
t.obs <- data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                    print_qtrans(msm_50_ob, 't1', 1, 2, trans12[1])) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                    print_qtrans(msm_50_ob, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                    print_qtrans(msm_50_ob, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                    print_qtrans(msm_50_ob, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                    print_qtrans(msm_50_ob, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_50_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_50_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_50_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_50_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_50_ob, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_ob, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_left_ob, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_left_ob, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_left_ob, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_left_ob, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_left_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_left_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_left_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_left_ob, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_left_ob, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_ob, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_50_4_ob, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_50_4_ob, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_50_4_ob, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_ob, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[04, 08)',
                       print_qtrans(msm_50_4_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[08, 12)',
                       print_qtrans(msm_50_4_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[12, 16)',
                       print_qtrans(msm_50_4_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_ob, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_50_4_ob, 2, 1))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_ob, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                      print_qtrans(msm_left_4_ob, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                      print_qtrans(msm_left_4_ob, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                      print_qtrans(msm_left_4_ob, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_ob, 't5', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_ob, 't1', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[04, 08)',
                      print_qtrans(msm_left_4_ob, 't2', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[08, 12)',
                      print_qtrans(msm_left_4_ob, 't3', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[12, 16)',
                      print_qtrans(msm_left_4_ob, 't4', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_ob, 't5', 2, 3, exp_param))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'Sp -> Sc: HR(FP)',
                       print_HR(msm_left_4_ob, 2, 1)))

t.obs %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
  select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

t.obs %>% filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

dgraf <- data.frame(Age = c(seq(1, 20, 0.1), rep(1:20, 9)), 
                    Transition = c(rep('Theoretical', 191), rep(10, 2*20), rep(4, 2*20),
                                   rep('Theoretical', 20), rep(10, 2*20), rep(4, 2*20)),
                    Left = c(rep('Theoretical', 191), rep(rep(c('No', 'Yes'), each = 20), 2),
                             rep('Theoretical', 20), rep(rep(c('No', 'Yes'), each = 20), 2)),
                    trans = rep(c('S0 -> Sp', 'Sp -> Sc'), c(271,100)),
                    hazard = c((shape_param/scale_param)*(seq(1, 20, 0.1)/
                                                            scale_param)^(shape_param - 1),
                               rep(t.obs$median[1:5], c(3:4, 4, 4:5)),
                               rep(t.obs$median[13:17], c(3:4, 4, 4:5)),
                               rep(t.obs$median[25:29], c(3:4, 4, 4:5)),
                               rep(t.obs$median[37:41], c(3:4, 4, 4:5)),
                               rep(exp_param, 20),
                               rep(t.obs$median[7:11], c(3:4, 4, 4:5)),
                               rep(t.obs$median[19:23], c(3:4, 4, 4:5)),
                               rep(t.obs$median[31:35], c(3:4, 4, 4:5)),
                               rep(t.obs$median[43:47], c(3:4, 4, 4:5))))
dgraf$Transition <- relevel(dgraf$Transition, ref = 'Theoretical')
dgraf$Left <- relevel(dgraf$Left, ref = 'Theoretical')
# ggplot(dgraf, aes(x = Age, y = hazard, col = Transition, lty = Left)) + geom_step() + 
#   facet_grid(trans ~ ., scales = "free")
grid.arrange(ggplot(dgraf %>% filter(trans == 'S0 -> Sp'),
                    aes(x = Age, y = hazard, lty = Left, color = Transition)) +
               geom_step() + ylim(0, 0.0021) + labs(y = 'Transition rate S0 -> Sp') +
               theme(legend.position = "none"),
             ggplot(dgraf %>% filter(trans == 'Sp -> Sc'),
                    aes(x = Age, y = hazard, lty = Left, color = Transition)) + geom_step() +
               ylim(0, 0.3) + labs(lty = 'Truncation', y = 'Transition rate Sp -> Sc'),
             nrow = 1)
tiff(filename = "fig_2.tiff", width = 20, height = 15, units = 'cm', res = 300)
grid.arrange(ggplot(dgraf %>% filter(trans == 'S0 -> Sp', Transition != 4),
                    aes(x = Age, y = hazard, lty = Left)) + geom_step() + ylim(0, 0.0021) +
               labs(y = 'Transition rate S0 -> Sp') + theme(legend.position = "none"),
             ggplot(dgraf %>% filter(trans == 'Sp -> Sc', Transition != 4),
                    aes(x = Age, y = hazard, lty = Left)) + geom_step() + ylim(0, 0.3) +
               labs(lty = 'Late Entry', y = 'Transition rate Sp -> Sc'),
             nrow = 1)
dev.off()
```

## 2-state model
### Model with event as SCD or IC. Time up to IC.
```{r, echo = F}
t.no <- data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                   print_qtrans(msm_50_no, 't1', 1, 2, trans12[1])) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                   print_qtrans(msm_50_no, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                   print_qtrans(msm_50_no, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                   print_qtrans(msm_50_no, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                   print_qtrans(msm_50_no, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_no, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_no, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_left_no, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_left_no, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_left_no, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_left_no, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_no, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_no, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_50_4_no, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_50_4_no, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_50_4_no, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_no, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_4_no, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_no, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                      print_qtrans(msm_left_4_no, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                      print_qtrans(msm_left_4_no, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                      print_qtrans(msm_left_4_no, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_no, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_4_no, 1, HR_FP)))

# t.no %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

t.no %>% filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

### Model with event as SCD or IC. Time up to next mamography.
```{r, echo = F}
t.si <- data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                   print_qtrans(msm_50_si, 't1', 1, 2, trans12[1])) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                   print_qtrans(msm_50_si, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                   print_qtrans(msm_50_si, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                   print_qtrans(msm_50_si, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                   print_qtrans(msm_50_si, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_si, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_left_si, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_left_si, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_left_si, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_left_si, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_left_si, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_si, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                       print_qtrans(msm_50_4_si, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[04, 08)',
                       print_qtrans(msm_50_4_si, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[08, 12)',
                       print_qtrans(msm_50_4_si, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[12, 16)',
                       print_qtrans(msm_50_4_si, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp', pci = '[16, Inf)',
                       print_qtrans(msm_50_4_si, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_50_4_si, 1, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[-Inf, 4)',
                      print_qtrans(msm_left_4_si, 't1', 1, 2, trans12[1]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[04, 08)',
                      print_qtrans(msm_left_4_si, 't2', 1, 2, trans12[2]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[08, 12)',
                      print_qtrans(msm_left_4_si, 't3', 1, 2, trans12[3]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[12, 16)',
                      print_qtrans(msm_left_4_si, 't4', 1, 2, trans12[4]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp', pci = '[16, Inf)',
                      print_qtrans(msm_left_4_si, 't4', 1, 2, trans12[5]))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'S0 -> Sp: HR(FP)',
                       print_HR(msm_left_4_si, 1, HR_FP)))

# t.si %>% filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, pci, bias:coverage) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)

t.si %>% filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

# Cox model
## Causa-específic
### Complet
```{r,echo=F}
t.ce_al <- data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                      print_cox(cox_50_al, 1, HR_FP)) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_4_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                      print_cox(cox_left_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_4_al, 2, HR_FP)))

t.ce_al %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, outcome, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, desc(outcome), est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

### Observed
```{r,echo=F}
t.ce_ob <- data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                      print_cox(cox_50_ob, 1, HR_FP)) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_4_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                      print_cox(cox_left_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_cox(cox_left_4_ob, 2, HR_FP)))

t.ce_ob %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, outcome, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, desc(outcome), est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

## 2-state model
### Model with event as SCD or IC. Time up to IC.
```{r, echo = F}
t.no <- data.frame(N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                       print_cox(cox_50_no, NULL, HR_FP)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                       print_cox(cox_left_no, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                       print_cox(cox_50_4_no, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                       print_cox(cox_left_4_no, NULL, HR_FP)))

# t.no %>% #filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, mean:p975) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('mean', 'median', 'p25', 'p975'), 4)

t.no %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

### Model with event as SCD or IC. Time up to next mamography.
```{r, echo = F}
t.si <- data.frame(N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_cox(cox_50_si, NULL, HR_FP)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                       print_cox(cox_left_si, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                       print_cox(cox_50_4_si, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                       print_cox(cox_left_4_si, NULL, HR_FP)))

# t.si %>% #filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, mean:p975) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('mean', 'median', 'p25', 'p975'), 4)

t.si %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

# Discret-time model
## Complet
```{r,echo=F}
t.disc_al <- data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                        print_disc(disc_50_al, 1, HR_FP)) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_4_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                      print_disc(disc_left_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_4_al, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_al, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_4_al, 2, HR_FP)))

t.disc_al %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, outcome, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, desc(outcome), est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

## Observed
```{r,echo=F}
t.disc_ob <- data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                        print_disc(disc_50_ob, 1, HR_FP)) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_4_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                      print_disc(disc_left_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'SCD', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_4_ob, 1, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_ob, 2, HR_FP))) %>%
  bind_rows(data.frame(outcome = 'IC', N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                   print_disc(disc_left_4_ob, 2, HR_FP)))

t.disc_ob %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, outcome, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, desc(outcome), est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

## 2-state model
### Model with event as SCD or IC. Time up to IC.
```{r, echo = F}
t.no <- data.frame(N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                       print_disc(disc_50_no, NULL, HR_FP)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                       print_disc(disc_left_no, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                       print_disc(disc_50_4_no, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                       print_disc(disc_left_4_no, NULL, HR_FP)))

# t.no %>% #filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, mean:p975) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('mean', 'median', 'p25', 'p975'), 4)

t.no %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```

### Model with event as SCD or IC. Time up to next mamography.
```{r, echo = F}
t.si <- data.frame(N_crib = 10, left_trunc = 'No', est = 'HR(FP)',
                   print_disc(disc_50_si, NULL, HR_FP)) %>%
  bind_rows(data.frame(N_crib = 10, left_trunc = 'Yes', est = 'HR(FP)',
                       print_disc(disc_left_si, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'No', est = 'HR(FP)',
                       print_disc(disc_50_4_si, NULL, HR_FP))) %>%
  bind_rows(data.frame(N_crib = 4, left_trunc = 'Yes', est = 'HR(FP)',
                       print_disc(disc_left_4_si, NULL, HR_FP)))

# t.si %>% #filter(stringr::str_sub(est, start = -6, end = -1) != 'HR(FP)') %>%
#   select(left_trunc, N_crib, est, mean:p975) %>% 
#   arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
#   formatRound(c('mean', 'median', 'p25', 'p975'), 4)

t.si %>%# filter(stringr::str_sub(est, start = -6, end = -1) == 'HR(FP)') %>%
  select(left_trunc, N_crib, est, bias:coverage) %>% 
  arrange(left_trunc, est, desc(N_crib)) %>% datatable %>%
  formatRound(c('bias_tp', 'coverage'), 2) %>% formatRound(c('bias', 'accuracy'), 4)
```
